Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-10-29 presentacion_hiram/presentacion-tesis.tex
nuevo

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Frankfurt}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\begin{document}
	\author{
		Departamento de Investigacion en F\'isica \\
		Maestr\'ia en Ciencias (F\'isica)\\
		Hiram Ernesto Dami\'an}
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
%	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	%\date{}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
	\begin{frame}
	\titlepage
\end{frame}

@@

\begin{frame}
\frametitle{Particles Properties}
Table of particles in SM
\begin{table}
\tiny{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|c|c|}
	\hline 
Particle	&Mass (MeV/$c^2$)  &Charge  & spin &Lifetime (s)  & Distance in lifetime (meters) \\ 
	\hline 
Up (u)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable &  -\\ 
	\hline 
Charm (c)	& 1280 &$\frac{2}{3}$  &  $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ &  5.21$\times 10^{-3}$ \\ 
	\hline 
Top	(t)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$  & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$   \\ 
	\hline 
Down (d)	& 4.6 &$-\frac{1}{3}$  & $\frac{1}{2}$  & Stable & - \\ 
	\hline 
Strange (s)	& 96 &$-\frac{1}{3}$  & $\frac{1}{2}$  &$1.24 \times 10^{-8}$  & 58.7 \\ 
	\hline 
Bottom (b)	& 4180 &$-\frac{1}{3}$  &  $\frac{1}{2}$ &$1.3 \times 10^{-12}$   & 6.16 $\times 10^{-3}$\\ 
	\hline 
W 	& 80379 &$\pm$1  & 1 & 3$\times$ 10$^{-25}$ &  1.42$\times 10^{-15}$\\ 
	\hline 
Z & 91187.6 &0  & 1 & 3$\times$ 10$^{-25}$  &1.42$\times 10^{-15}$ \\ 
\hline
Photon ($\gamma$) & 0 &0  &  1&Stable  & - \\ 
\hline
Gluon (g)	& 0 &0  &  1&Stable  & - \\ 
	\hline 
Higgs (H)	& 125.18 &0  &  0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
	\hline 
Electron (-e)& 0.511 & -1 &   $\frac{1}{2}$& Stable & - \\ 
	\hline 
Muon ($\mu$)	& 105.7 & -1  &  $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
	\hline 
$\tau$	& 1776.86 &-1  &  $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 
	\hline 
$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 &  $\frac{1}{2}$ & Stable &  -\\ 
	\hline 
\end{tabular} 
}
\end{table}
\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
\end{frame}

@@

\begin{frame}
\section{Production cross section}
\frametitle{Cross section}
\begin{itemize}
\item Classical definition: When two particles interact, cross section is the area transverse to their relative motion within
which they must meet in order to scatter from each other.
\item Quantum definition: Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
\item Experimentally
\begin{align}
d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Cross section}
\begin{center}\begin{center}

	\end{center}
	\begin{figure}
		\includegraphics[scale=0.5]{figures/cs1.png}
		\caption{Drawing of an idealized scattering process showing the differential solid angle $\Delta\Omega$ and the
			scattering angle $\theta$}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Cross section}
The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
\begin{align}
N_R=\sigma \text{L}
\end{align}
\end{frame}

@@

\begin{frame}
\frametitle{Higgs production cross section}
\begin{center}
\begin{figure}
\includegraphics[scale=0.42]{figures/7-14xsec.eps}
\caption{ Higgs boson production cross sections as a function of the centre-of-mass-energies}	
\end{figure}
\end{center}
\end{frame}

@@

\begin{frame}
\frametitle{Higgs Branching ratio}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.35]{figures/Higgs_BR_120-130_7.eps}
		\caption{Standard Model Higgs boson decay branching ratios}	
	\end{figure}
\end{center}
\end{frame}

@@

\begin{frame}
\frametitle{LHC}
\begin{center}
	\begin{figure}
	\includegraphics[scale=0.25]{figures/CERN's-accelerator-complex2013.jpg}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{LHC parameters}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.5]{figures/lhc-t.png}
		\caption*{Table. LHC characteristics for run 2.}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{LHC}
\begin{table}
	\caption*{Accelerator operation energies}
	\begin{tabular}{|c|c|}
		\hline
		Accelerator & Energy \\
		\hline
		Linac 2 &  50 MeV \\
		\hline
		PS Booster & 1.4 GeV \\
		\hline
		Proton Scyncroton (PS) & 25 GeV\\
		\hline
		SPS &  450 GeV\\
		\hline
		LHC & 6.5 TeV\\
		\hline
	\end{tabular}
\end{table}
\end{frame}

@@

@@

\begin{multicols}{2}
\tiny{
\begin{itemize}
\item t$\rightarrow$W$^+$b$\rightarrow$ $l^+ \nu_\mu$b
\item H$\rightarrow$ W$^+$W$^-$

\begin{list}{--}{}
\item  \tiny{W$\rightarrow$ $l^\pm \nu$, where l can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
\item   \tiny{W$\rightarrow$ q$\bar{q}$}
\item \tiny{W bosons decay leptonically resulting in a signature of two same-sign leptons }
\end{list}
\item a light-flavor quark 
\item  b quark jet  \cite{2}
\end{itemize}
}
\columnbreak
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/jet.png}
\end{figure}
\end{multicols}
\end{frame}

\begin{frame}
\frametitle{Event selection}
The main analysis strategy is to obtain a selection of events compatible with
certain characteristics of the signal at pre-selection level.\\

It is required:
\begin{itemize}
\item The events are selected those that contain two leptons ($l^+l^-$)  with the same sign.
\item Transverse moment $p_{t}$ > 25 and 15 GeV, for the muons.
\item A foward jet with $p_t$ > 40 GeV, | $\eta$ | > 2.4
\item One or more b-jets with (| $\eta$ | <2.4)\cite{1}
\end{itemize}
\end{frame}

\nologo{
\begin{frame}
\frametitle{Previous results for t$\bar{t}$H+$tH$ production}
\begin{multicols}{2}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.4]{figures/tth-table.png}
		\caption*{}
	\end{figure}
\end{center}
\columnbreak
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.3]{figures/bdt.png}
		\caption*{\tiny{Post-fit categorized BDT classifier outputs as used in
			the maximum likelihood fit for the $\mu\mu$ channel for
			35.9 fb$^{-1}$.In the box below each distribution, the ratio
			of the observed and predicted event yields is shown.\cite{2}
		 }}
	\end{figure}
\end{center}
\end{multicols}
\end{frame}
}
\begin{frame}
	\begin{center}
		\begin{figure}
			\includegraphics[scale=0.3]{figures/sc.png}
			\caption{Observed and expected 95$\%$ C.L. upper limit on the $tH$ + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ . The expected limit is derived from a background-only MC dataset.}
		\end{figure}
	\end{center}
\end{frame}

\begin{frame}
\frametitle{Main backgrounds}
\begin{center}
\scriptsize{
\begin{tabular}{|c|c|p{7cm}|}
	\hline
	Background & $\sigma$[pb] & Decay process \\
	\hline
t$\bar{t}$H	& 0.2151 & t$\bar{t}$H $\rightarrow$ W$^+$b W$^- \bar{b}$ W$^+$W$^-$ $\rightarrow$ $\mu^+ \nu_\mu$b$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
\hline  
t$\bar{t}$W  &0.2043 &t$\bar{t}$W  $\rightarrow$  W$^+$bW$^- \bar{b}$ $\mu^+\nu_\mu$ $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$\\
\hline
 t$\bar{t}$Z & 0.2529 & t$\bar{t}$Z  $\rightarrow$ W$^+$b  W$^-$$\bar{b} \mu^+ \mu^-$ $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}\mu^+ \mu^-$  \\
 \hline 
  W$^+$W$^-$  &1.64 & W$^+$W$^-$ $\rightarrow$$\mu^+\nu_\mu$$\mu^-\bar{\nu_\mu}$ \\
    \hline 
  tZq  &0.0758 & tZq$\rightarrow$W$^+$b$\mu^+ \mu^-$ q$\rightarrow$$\mu^+ \nu_\mu$b $\mu^+\mu^-$ q \\
    \hline 
  t$\bar{t}$t$\bar{t}$  & 0.0091&t$\bar{t}$t$\bar{t}$ $\rightarrow$ W$^+$b   W$^- \bar{b}$  W$^+$b  W$^- \bar{b}$   $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$b   $\mu^- \bar{\nu_\mu} \bar{b}$ \\
    \hline 
  W$^+$W$^-$Z  & 0.1651& W$^+$W$^-$Z$\rightarrow$ $\mu^+ \nu_\mu$ $\mu^- \bar{\nu_\mu} \mu^+ \mu^-$\\
    \hline 
 ZZZ  &0.0139 & ZZZ$\rightarrow$ $\mu^+ \mu^-\mu^+ \mu^-l^+ l^-$  \\
    \hline 
  W$^+$ZZ  & 0.0556&W$^+$ZZ$\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^- l^+l^-$ \\
  \hline 
 W$^+$Z &4.42965 &W$^+$Z$\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
 \hline
ZZ &  1.256 &ZZ$\rightarrow$ $\mu^+ \mu^- \mu^+ \mu^-$ \\
 \hline
\end{tabular}
}
\end{center}
\tiny{
\begin{itemize}
	\item Rare SM: tttt,WWW,WWZ,WZZ,WW,tZq
	\item WZ:WZ,ZZ
\end{itemize}}
\end{frame}

\begin{frame}
\frametitle{Boosted decision tree (BDT)}
\begin{itemize}
\item A decision tree takes a set of input features and splits input data recursively based on
those features.
Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.
\item The BDT training is performed using several event variables for signal and background. 
	\item BDT training uses MC samples for  t$\bar{t}$W$^\pm$ and t$\bar{t}$Z (t$\bar{t}$V),
	because t$\bar{t}$V is one of the biggest backgrounds
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Uncertainty values}
Common uncertainties for MC :
\begin{itemize}
	\item Muon identificacion 6$\%$
	\item Dimuon Trigger  1$\%$ 
	\item Luminosity measurement: ~2.6$\%$.
\end{itemize}
\begin{table}
			\renewcommand{\arraystretch}{0.1}
	\begin{tabular}{|c|M{2.7cm}|M{2.3cm}|}
\hline
\scriptsize{Background}& \scriptsize{Sources of systematic uncertainty}& \scriptsize{Total Systematic Uncertainty} \\
\hline
\rule{0pt}{3pt}t$\bar{t}$H  &{\begin{itemize} \tiny{ 
 	\item PDF 4$\%$ \\
 	\item QCD scale 5.8$\%$ \\
 	\item Higgs BR  1$\%$ }
\end{itemize}}  & 9.36$\%$ \\
 \hline  
 t$\bar{t}$Z&{\begin{itemize} \tiny{ 
 			\item PDF 4$\%$ \\
 			\item QCD scale 10$\%$ \\
 			 }
 \end{itemize}} & 12.36 $\%$ \\
 \hline
 t$\bar{t}$W&{\begin{itemize} \tiny{ 
 			\item PDF 4$\%$ \\
 			\item QCD scale 12$\%$ \\
 		}
 \end{itemize}} &14.03 $\%$ \\
 \hline
\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\begin{table}
		\renewcommand{\arraystretch}{0.1}
	\begin{tabular}{|c|M{2.7cm}|M{2.3cm}|}
\hline
\scriptsize{Background}& \scriptsize{Sources of systematic uncertainty}& \scriptsize{Total Systematic Uncertainty} \\
		\hline
	 \tiny{Rares SM} & {\begin{itemize} \tiny{
				\item Rare SM 50$\%$ }
	\end{itemize}}&50.36 $\%$ \\
	\hline
	\tiny{WZ} & {\begin{itemize}\tiny{
				\item Sample modelling and statistics 50$\%$ }
	\end{itemize}} & 50.36$\%$ \\
	\hline 
	\tiny{Non prompt leptons} &{\begin{itemize} \tiny{
				\item Fake rate estimation 50$\%$
				\item Closure 7$\%$ }
	\end{itemize}} 		 & 50.48$\%$ \\
	\hline 
	\end{tabular}
\end{table}

@@

\begin{frame}
\frametitle{Likelihood model}
The likelihood function is the product of Poisson probabilities for all bins
\begin{align}
L(\mu,\theta)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)}
\end{align}

\begin{itemize}
	\item	N=number of bins
	\item	$\mu$=parameter of signal
	\item	s=signal
	\item	b=background
	\item	n=number of events
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Results}
\framesubtitle{Likelihood scan}
To test a hypothesized value of $\mu$ we consider the profile likelihood ratio
\begin{align}
\lambda(\mu)=\frac{L(\mu,\hat{\hat{\theta}})}{L(\hat{\mu},\hat{\theta})}
\end{align}
\small{
	\begin{itemize}
		\item Here $\hat{\hat{\theta}} $ in the numerator denotes the value of $\theta$ that maximizes L for the specified $\mu$,
		it is the conditional maximum-likelihood (ML) estimator of $\hat{\theta}$ (and thus is a function of $\mu$).
		The denominator is the maximized (unconditional) likelihood function, i.e., $\hat{\mu}$ and $\hat{\theta}$ are
		their ML estimators\cite{3}. 
		\item The presence of the nuisance parameters broadens the profile likelihood as a
		function of $\mu$ relative to what one would have if their values were fixed. This reflects the loss
		of information about $\mu$ due to the systematic uncertainties\cite{3}\cite{4}. 
	\end{itemize}
}
\end{frame}

\begin{frame}
\frametitle{Statistical test}
It is convenient to use the statistic
\begin{align}
t_\mu=-2\ln{\lambda(\mu)} 
\end{align}
as the basis of a statistical test. Higher values of $t_\mu$ thus correspond to increasing
incompatbility between the data and $\mu$.
We may define a test of a hypothesized value of $\mu$ by using the statistic $t_\mu$ directly
as measure of discrepancy between the data and the hypothesis, with higher values of
$t_\mu$ correspond to increasing disagreement\cite{4}
\end{frame}

>>>>

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Frankfurt}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\begin{document}
	\author{
		Departamento de Investigacion en F\'isica \\
		Maestr\'ia en Ciencias (F\'isica)\\
		Hiram Ernesto Dami\'an}
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	%\date{}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
	\begin{frame}
	\titlepage
\end{frame}

@@

\begin{frame}
\frametitle{Particles Properties}
Table of particles in SM
\begin{table}
\tiny{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
	\hline 
	Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance in lifetime (meters) \\ 
	\hline 
	Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
	\hline 
	Charm ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
	\hline 
	Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
	\hline 
	Down ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
	\hline 
	Strange ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
	\hline

	Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
	\hline 
	$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.42$\times 10^{-15}$\\ 
	\hline 
	$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.42$\times 10^{-15}$ \\ 
	\hline
	Photon ($\gamma$) & 0 &0 & 1&Stable & - \\ 
	\hline
	Gluon ($g$)	& 0 &0 & 1&Stable & - \\ 
	\hline 
	Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
	\hline 
	Electron ($e$)& 0.511 & -1 &  $\frac{1}{2}$& Stable & - \\ 
	\hline 
	Muon ($\mu$)	& 105.7 & -1 & $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
	\hline 
	$\tau$	& 1776.86 &-1 & $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 
	\hline 
	$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
	\hline 
\end{tabular} 
}
\end{table}
\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
\end{frame}

@@

\begin{frame}
\section{Production cross section}
\frametitle{Cross section}
\begin{itemize}
\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
\item Experimentally
\begin{align}
d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
\begin{align}
N_R=\sigma \text{L}
\end{align}
\end{itemize}
\end{frame}

@@

@@

@@

\begin{frame}
\frametitle{LHC}
	\begin{figure}
		\centering
	\includegraphics[scale=0.2]{figures/CERN's-accelerator-complex2013.jpg}
	\end{figure}
\end{frame}

\begin{frame}
\frametitle{LHC parameters}
\begin{minipage}[c]{0.48\textwidth}
	\small
	\begin{figure}
	\centering
	\includegraphics[scale=0.4]{figures/lhc-t.png}
	\caption*{Table. LHC characteristics for run 2.}
\end{figure}
\end{minipage}
\hfill
\begin{minipage}[c]{0.48\textwidth}
	\small
	\begin{table}
		\centering
		\caption*{Accelerator operation energies}
		\begin{tabular}{|c|c|}
			\hline
			Accelerator & Energy \\
			\hline
			Linac 2 &  50 MeV \\
			\hline
			PS Booster & 1.4 GeV \\
			\hline
			Proton Scyncroton (PS) & 25 GeV\\
			\hline
			SPS &  450 GeV\\
			\hline
			LHC & 6.5 TeV\\
			\hline
		\end{tabular}
	\end{table}
\end{minipage}
\end{frame}

@@

\begin{frame}
\frametitle{LHC}
\begin{figure}[ht!]
	\centering
	\includegraphics[scale=0.6]{figures/csc.png}
	\caption*{Slide view of the CMS in terms of pseudorapidity $\eta=-\ln\left[\tan\left(\frac{\theta}{2}\right)\right]$}
\end{figure}
\end{frame}

@@

\begin{multicols}{2}
	\small{
\begin{itemize}
\item $t\rightarrow W$$^+$b$\rightarrow$ $l^+ \nu_\mu b$
\item $H\rightarrow$ $W^+$$W^-$

\begin{list}{--}{}
\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
\item   \small{$W\rightarrow$ $q\bar{q}$}
\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
\end{list}
\item a light-flavor quark 
\item  A b-jet  
\end{itemize}
}
\columnbreak
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/jet.png}
\end{figure}
\end{multicols}
\end{frame}

\begin{frame}
\frametitle{Event selection}
In order to detect signal events and reject background, the following selections are applied. 
\begin{itemize}
	\item The events must contain two muons with the same sign.
	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
	\item One or more b-tagged jets with $|\eta|$ < 2.4
\end{itemize}
\end{frame}

\nologo{
\begin{frame}
\frametitle{Previous results for $t\bar{t}H$+$tH$ production}

\begin{minipage}[c]{0.45\textwidth}
\begin{figure}
	\centering
	\includegraphics[scale=0.3]{figures/histo.png}
	\caption*{\tiny{Pre-fit classifier outputs for same sign dimuon, for training against $t\bar{t}V$ }}
\end{figure}
\end{minipage}
\hfill
\begin{minipage}[c]{.45\textwidth}
	\begin{figure}	\centering
	\includegraphics[width=\textwidth]{figures/sc.png}
	\caption*{\tiny{Observed and expected 95$\%$ C.L. upper limit on the tH + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ . The expected limit is derived from a background-only MC dataset.}}
	\end{figure}
\end{minipage}
\end{frame}
}

\begin{frame}
\begin{minipage}[b]{.48\textwidth}
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{figures/kos.png}
\end{figure}
\end{minipage}
\hfill
\begin{minipage}[b]{.48\textwidth}
	\begin{figure}
		\centering
		\includegraphics[width=\textwidth]{figures/kos2.png}
	\end{figure}
\end{minipage}
\begin{center}
\small{SM signal and backgrounds (Left) and $k_t$=-1 model (Right).}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Main backgrounds}
\tiny
\begin{table}
	\caption{Main backgrounds and their same sign $\mu\mu$ decay process }
\centering
\begin{tabular}{|c|l|}
	\hline
	Background & Decay process \\
	\hline
	$t\bar{t}W$ &$t\bar{t}W$ $\rightarrow$ $W^+ b W^- \bar{b}$ $\mu^+\nu_\mu$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$\\
	\hline
	$t\bar{t} Z$ & $t\bar{t} Z$ $\rightarrow$ $W^+ b$ $W^-\bar{b} \mu^+ \mu^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}\mu^+ \mu^-$ \\
	\hline
	$W^+ Z$ &$W^+ Z \rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
	\hline 
	$W^\pm$ $W^\pm$ & $W^+W^+$ $\rightarrow$$\mu^+\nu_\mu$$\mu^+ {\nu_\mu}$ \\
	\hline 
	$tZq$ & $tZq$ $\rightarrow$ $W^+$ $ b\mu^+ \mu^- q$ $\rightarrow$$\mu^+ \nu_\mu b$ $\mu^+\mu^- q$ \\
	\hline 
	$t\bar{t}t\bar{t}$ &$t\bar{t}t\bar{t}$ $\rightarrow$ $W^+ b$ $W^- \bar{b}$ $W^+ b$ $W^- \bar{b}$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ \\
	\hline 
	$W^+ W^- Z$ & $W^+ W^-$ $Z \rightarrow$ $\mu^+ \nu_\mu$ $\mu^- \bar{\nu_\mu} \mu^+ \mu^-$\\
	\hline 
	$ZZZ$ & $ZZZ \rightarrow$ $\mu^+ \mu^-\mu^+ \mu^-l^+ l^-$ \\
	\hline 
	$W^+ZZ$ &$W^+ZZ$ $\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^- l^+l^-$ \\
	\hline 
	$tZW^+$ & $tZW^+ \rightarrow$ $W^+b \mu^+ \mu^- \mu^+ \nu_\mu \rightarrow \mu^+ \nu_\mu b \mu^+ \mu^- \mu^+ \nu_\mu$\\
	\hline
	$ZZ$ & $ZZ\rightarrow$ $\mu^+ \mu^- \mu^+ \mu^-$ \\
	\hline
	$t\bar{t}H$	& $t\bar{t}H$ $\rightarrow W^+b W^- \bar{b} W^+W^-$ $\rightarrow$ $\mu^+ \nu_\mu b$$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
	\hline 
\end{tabular}
\label{back}
\end{table} 
\end{frame}

\begin{frame}
\frametitle{Signal and Backgrounds}
\begin{table}
	\centering
	\caption*{{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
			The uncertainties of yields include statistical and systematic \cite{2}}} 
	\begin{tabular}{cc}
		\hline
		Process & Number of events \\
		\hline
		$t\bar{t}W$ & 68 $\pm$ 10 \\
		$t\bar{t}Z$ & 25.9 $\pm$ 3.9\\
		$WZ$ & 15.1$\pm$7.7\\
		Rares & 20.9 $\pm$ 4.9\\
		Fakes & 80.9 $\pm$9.4\\
		$t\bar{t}H$ & 24.2 $\pm$ 2.1 \\
		\hline
		$tH$ (SM) & 2.14 $\pm$ 0.13\\
		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
	\end{tabular}	
	\label{tth-table}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Systematic uncertainties}
\begin{itemize}
	\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
	\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
	\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
	\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
	\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
\end{itemize}

\end{frame}
\begin{frame}
\frametitle{Boosted decision tree (BDT)}
\begin{itemize}
\item A decision tree takes a set of input features and splits input data recursively based on
those features.
Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.
\item The BDT training is performed using several event variables for signal and background. 
\end{itemize}
\end{frame}

@@

@@

\begin{frame}
\frametitle{Likelihood model}
The likelihood function is the product of Poisson probabilities for all bins
\begin{align}
	L(\mu,\alpha)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)} \prod_{k=1}^M e^{\frac{-\alpha^2_k}{2}}
\end{align}
	where $N$ is the total number of bins, $n_j$ is the number of events in a bin $j$, $s_j$ is the number of signal events, $\mu$ is a parameter that modifies the signal strength and $b_j$ is the number of background events.
	$b_j$ is the sum of different background processes $k$
\begin{align}
b_j=\sum_k^M b_j^k(1+ \alpha_k \sigma_k)
\end{align}
$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background. $\sigma_k$ for the backgrounds are shown in the Table of yields.
\end{frame}

\begin{frame}
\frametitle{Results}
	The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$. The minimization is performed by using the package ROOFIT. In the next slides, it shows the results of the model fitting using the Asimov data for the SM and the $k_t=-1$.
\end{frame}

\begin{frame}
\frametitle{Results}
\begin{minipage}{0.4\textwidth}
	\begin{center}
	\begin{figure}
		\includegraphics[width=5.5cm,height=5cm]{figures/simple.png}
		\caption*{\tiny{Post-fit signal and background yields for tH process in the SM. In the
			box below each distribution, the ratio of the observed and  event yields is shown}}
	\end{figure}
\end{center}
\end{minipage}\hfill \quad
\begin{minipage}{0.4\textwidth}
	\begin{center}
	\begin{figure}
		\includegraphics[width=5.5cm,height=5cm]{figures/simple-kt-1.png}
		\caption*{\tiny{Post-fit signal and background yields for tH process in the $k_t$=-1. In the
			box below each distribution, the ratio of the observed and event yields is shown}}
	\end{figure}
\end{center}
\end{minipage}
\end{frame}
